Increasing the topological gap by an order of magnitude through the geomerty for Majorana SNS junctions.

### 2018-12-04 paper/snakemajoranas.tex
Removed parentheses from mu
Added some topology talk

%%██████████████████████████████████████████████████████████████████████████
%%██ Physical picture
%%██████████████████████████████████████████████████████████████████████████
\section{Physical picture}
We consider a system [\ref{fig:setup}] consisting of a two dimensional strip of semiconductor, with superconductors adjacent on both sides.
A magnetic field pointed along the x direction is applied.
We model the system with a BdG hamiltonian; the normal part also has Rashba spin-orbit coupling and a Zeeman field, and the superconductors differ in superconducting phase.
For the zigzag geometry, we take a sawtooth like pattern wher $z_x$ is periodicity, $z_y$ the amplitude and W the width of the junction.
\begin{small}
\begin{align}
    H = \left(\frac{\hbar^2\left(\kx^2 + \ky^2\right)}{2\meff} - \mu\right)\tau_z+
        E_\text{z} \sigma_z+
        \alpha \left( \ky \sigma_x - \kx \sigma_y \right) \tau_z +
        \Delta \tau_y
\end{align}
\label{eq:hamiltonian}
\end{small}

@@

\begin{align}
    \gamma_j &= \frac{q+i k_{j} \tan \left(\frac{W k_{j}}{2}\right)}{q-i k_{j} \tan \left(\frac{W k_{j}}{2}\right)} \\
    \delta_j &= \frac{q-i k_{j} \cot \left(\frac{W k_{j}}{2}\right)}{q+i k_{j} \cot \left(\frac{W k_{j}}{2}\right)}\\
    e^{i \nu_{\arg}} &= \frac{E_\text{z} e^{i \theta }-i \alpha  k_x}{\sqrt{E_\text{z}^2+\alpha  k_x \left(\alpha  k_x-2 E_\text{z} \sin (\theta )\right)}}
\end{align}
\begin{footnotesize}
\begin{align}
    q &= \left[ \frac{2 m_\ast}{\hbar ^2}\left(\mu_s\right) - k_x^2 \right]^\frac{1}{2}\\
    k_1 &= \left[ \frac{2 m_\ast}{\hbar^2} \left(\mu_n-\sqrt{E_z^2-2 \alpha  E_z \sin (\theta ) k_x+\alpha ^2 k_x^2}\right) - k_x^2 \right]^\frac{1}{2}\\
    k_2 &= \left[ \frac{2 m_\ast}{\hbar^2} \left(\mu_n+\sqrt{E_z^2-2 \alpha  E_z \sin (\theta ) k_x+\alpha ^2 k_x^2}\right) - k_x^2 \right]^\frac{1}{2}
\end{align}
\end{footnotesize}

>>>>

%%██████████████████████████████████████████████████████████████████████████
%%██ Physical picture
%%██████████████████████████████████████████████████████████████████████████
\section{Physical picture}
We consider a system [\ref{fig:setup}] consisting of a two dimensional strip of semiconductor, with superconductors adjacent on both sides.
A magnetic field pointed along the x direction is applied.
We model the system with a BdG Hamiltonian[\ref{eq:hamiltonian}]; the normal part also has Rashba spin-orbit coupling and a Zeeman field, and the superconductors differ in superconducting phase.
For the zigzag geometry, we take a sawtooth like pattern wher $z_x$ is periodicity, $z_y$ the amplitude and $W$ the width of the junction.
We know from [\cite{pientka2017topological}] that the non-zigzag system is in class BDI.
Using the software package qsymm, we evaluate the symmetry class of the system to be D.

\begin{small}
\begin{align}
    H = \left(\frac{\hbar^2\left(\kx^2 + \ky^2\right)}{2\meff} - \mu\right)\tau_z+
        E_\text{z} \sigma_z+
        \alpha \left( \ky \sigma_x - \kx \sigma_y \right) \tau_z +
        \Delta \tau_y
\end{align}
\label{eq:hamiltonian}
\end{small}

@@

\begin{align}
    \gamma_j &= \frac{q+i k_{j} \tan \left(\frac{W k_{j}}{2}\right)}{q-i k_{j} \tan \left(\frac{W k_{j}}{2}\right)} \\
    \delta_j &= \frac{q-i k_{j} \cot \left(\frac{W k_{j}}{2}\right)}{q+i k_{j} \cot \left(\frac{W k_{j}}{2}\right)}\\
    e^{i \nu_{\arg}} &= \frac{E_\text{z} e^{i \theta }-i \alpha  k_x}{\sqrt{E_\text{z}^2+\alpha  k_x \left(\alpha  k_x-2 E_\text{z} \sin (\theta )\right)}}
\end{align}
\begin{footnotesize}
\begin{align}
    q &= \left[ \frac{2 m_\ast}{\hbar ^2}\mu_s - k_x^2 \right]^\frac{1}{2}\\
    k_1 &= \left[ \frac{2 m_\ast}{\hbar^2} \left(\mu_n-\sqrt{E_z^2-2 \alpha  E_z \sin (\theta ) k_x+\alpha ^2 k_x^2}\right) - k_x^2 \right]^\frac{1}{2}\\
    k_2 &= \left[ \frac{2 m_\ast}{\hbar^2} \left(\mu_n+\sqrt{E_z^2-2 \alpha  E_z \sin (\theta ) k_x+\alpha ^2 k_x^2}\right) - k_x^2 \right]^\frac{1}{2}
\end{align}
\end{footnotesize}
